PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-27 paper.tex
Update on Overleaf.

%% Original abstract -- kept for future reference
%Over the last decades, efforts around the world have sought to improve
%human-robot interactions, more recently with a focus on longer-term
%interactions. If worthy, these efforts are often incremental and many
%problems remain. In the light of the recent and rapid progress of machine
%learning, we propose here to shift the paradigm: instead of more and more
%complex symbolic cognitive modeling of the interactions between humans and
%robots, we argue that natural and sustainable human-robot interaction could
%instead be directly learned from actual human-human interactions. This paper
%outlines the main challenges ahead, and proposes a first concrete step
%toward the operationalization of this novel paradigm: the creation of a
%large dataset of human-robot social interactions, suitable for machine
%learning.

Child-robot interactions are increasingly being explored in domains which
require longer-term application, such as healthcare and education. In order
for a robot to behave in an appropriate manner over longer timescales, its
behaviours should be coterminous with that of the interacting children.
Generating such sustained and engaging social behaviours is an on-going research
challenge, and we argue here that the recent progress of deep machine learning
opens new perspectives that the Human-Robot Interaction (HRI) community
should embrace.

As an initial step in that direction, we introduce a novel
open dataset of children social interactions, designed with
deep-learning applications in mind. Our acquisition methodology relies on
engaging and purposefully underspecified \emph{free play} situations. By doing
so, we capture a rich set of behavioural patterns occurring in natural
social interactions. Learning to recognise (and generate) automatically such
behaviours is one of the ambitious foreseen outcome that this dataset enables.

>>>>

%% Original abstract -- kept for future reference
%Over the last decades, efforts around the world have sought to improve
%human-robot interactions, more recently with a focus on longer-term
%interactions. If worthy, these efforts are often incremental and many
%problems remain. In the light of the recent and rapid progress of machine
%learning, we propose here to shift the paradigm: instead of more and more
%complex symbolic cognitive modeling of the interactions between humans and
%robots, we argue that natural and sustainable human-robot interaction could
%instead be directly learned from actual human-human interactions. This paper
%outlines the main challenges ahead, and proposes a first concrete step
%toward the operationalisation of this novel paradigm: the creation of a
%large dataset of human-robot social interactions, suitable for machine
%learning.

Child-robot interactions are increasingly being explored in domains which
require longer-term application, such as healthcare and education. In order
for a robot to behave in an appropriate manner over longer timescales, its
behaviours should be aligned and meaningful to the interacting children.
Generating such sustained and engaging social behaviours is an on-going research
challenge, and we argue here that the recent progress of deep machine learning
opens new perspectives that the Human-Robot Interaction (HRI) community
should embrace.

As an initial step in that direction, we introduce a novel,
open dataset of children social interactions, designed with
machine learning applications in mind. Our data acquisition methodology relies on
a engaging and purposefully underspecified \emph{free play} interaction. By doing
so, we capture a rich set of behavioural patterns occurring in natural
social interactions. Learning to recognise, and possibly generate, such
behaviours is one of the future research direction that we foresee this dataset to effectively support.
